Refunctionalization of Abstract Abstract Machines (Functional Pearl)

### 2018-06-14 paper/paper.tex
update color; minor revision

\textbf{Cache-Passing Style.}
We can now transform our interpreter into cache-passing style. We begin by changing the 
return type @Ans@ to a case class which contains a @VS@ set and a cache. @Ans@ also supports
its own accumulating operation @++@ which defines as union on @Set[VS]@ and join on caches.
% TODO join?
\begin{lstlisting}
                case class Ans(vss: Set[VS], cache: Cache) {
                  def ++(ans: Ans): Ans = { Ans(vss ++ ans.vss, cache.join(ans.cache)) }
                }
\end{lstlisting}

>>>>

\textbf{Cache-Passing Style.}
We can now transform our interpreter into cache-passing style. We begin by changing the 
return type @Ans@ to a case class which contains a @VS@ set and a cache. @Ans@ also implements 
its own accumulating operation @++@ which defines as union on @Set[VS]@ and join on caches.
The join operation of caches is defined as joining its two store components.

\begin{lstlisting}
                case class Ans(vss: Set[VS], cache: Cache) {
                  def ++(ans: Ans): Ans = { Ans(vss ++ ans.vss, cache.join(ans.cache)) }
                }
\end{lstlisting}
